Invasive lionfish present region-wide variation of allometric growth in the

### 2018-04-20 docs/Manuscript.Rmd
Changed geom_text to geom_annotate to have a better annotation of the equation

```{r}
get_eqn <- function(model){
  substitute(italic(TW) == a %*% italic(TL)^b,
             list(a = format(10^coef(model)[1], digits = 3),
                  b = format(coef(model)[2], digits = 3))) %>% 
    as.expression() %>% 
    as.character()
}

@@

fit <- ggplot(data = fish, mapping = aes(x = Length, y = Weight)) +
  geom_point(size = 3, shape = 21, fill = "steelblue", color = "black") +
  theme_cowplot() +
  labs(x = "Total length (mm)", y = "Total Weight (gr)") +
  theme(text = element_text(family = "Times")) +
  scale_color_brewer(palette = "Set3") +
  theme(text=element_text(family = "Times")) +
  geom_smooth(method = "lm", formula = y ~ I(a*x^b), color = "black", se = F) +
  geom_text(aes(x = 120, y = 390), label = get_eqn(model), parse = T, size = 4, family="Times", face="italic") +
  geom_text(aes(x = 120, y = 350), label = get_rsq(model), parse = T, size = 4, family="Times", face="italic")

>>>>

```{r}
get_eqn <- function(model){
  substitute(italic(TW) == a %*% "10"^"-6" ~ italic(TL)^b,
             list(a = "3.2",
                  b = format(coef(model)[2], digits = 3))) %>% 
    as.expression() %>% 
    as.character()
}

@@

fit <- ggplot(data = fish, mapping = aes(x = Length, y = Weight)) +
  geom_point(size = 3, shape = 21, fill = "steelblue", color = "black") +
  theme_cowplot() +
  labs(x = "Total length (mm)", y = "Total Weight (gr)") +
  theme(text = element_text(family = "Times")) +
  scale_color_brewer(palette = "Set3") +
  theme(text=element_text(family = "Times")) +
  geom_smooth(method = "lm", formula = y ~ I(a*x^b), color = "black", se = F) +
  annotate(geom = "text",
            x = 120, y = 390,
            label = get_eqn(model),
            parse = T,
            size = 4,
            family="Times",
            face="italic") +
  annotate(geom = "text",
            x = 120, y = 350, 
            label = get_rsq(model),
            parse = T,
            size = 4,
            family="Times",
            face="italic")
